---
title: "AirQualityPlottingApp"
author: "Christopher Brodowski"
date: "July 8, 2017"
output:
  ioslides_presentation:
    fig_width: 1
    fig_height: 1
    fig_retina: 1
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Air Quality Data Plotter

This program will allow the user to display time series plots of daily air quality measurements in New York, from May to September of 1973.

- Ozone (ppb)
- Temperature (degrees F)
- Wind Speed (mph)
- Solar Radiation (lang)

NOTE: Plots displayed in presentation have less detail than in the actual application.

## Sample Of Usage
```{r include=FALSE, cache=FALSE}
library(datasets)
library(plotly)
require(data.table)
library(dplyr)
library(DT)
```
```{r echo=FALSE}
localAQ = airquality
# Add a new time field
timeVect <- vector('character', length=0)
for (i in 1:nrow(localAQ)) {
	strr <- sprintf("%02d/%02d/73", localAQ$Month[i], localAQ$Day[i])
	timeVect <- c(timeVect, strr)
}
localAQ$Time <- as.Date(timeVect, format="%m/%d/%y")
inputPanel(
  selectInput("StartTime", "Start Date", 
				choices=seq(as.Date("1973-05-01"), as.Date("1973-09-29"), "days")),
	selectInput("EndTime", "End Date",
				choices=seq(as.Date("1973-05-01"), as.Date("1973-09-29"), "days")),
	selectInput("PlottingVariable", "What Variable to Plot?",
				choices=c("Ozone", "Solar.R", "Temp", "Wind")),
  checkboxInput("Proceed", "Proceed?")
)
renderPlot({
  if (input$Proceed) {
  		# Get the right time
    #print("entering plotter")
  		if (input$StartTime < input$EndTime) {
  			first <- input$StartTime
  			second <- input$EndTime
  		} else {
  			first <- input$EndTime
  			second <- input$StartTime
  		}
  		subsettedData <- subset(localAQ, Time >= first & Time <= second)
  		
  		# TODO: Remove missing data?
  		outputVar <- input$PlottingVariable
  		x <- list(title="Date", titlefont=list(family="Courier New", 
  		                                       size=16))
  		y <- list(title=outputVar, titlefont=list(family="Courier New", 
  		                                          size=16))
  		#dev.off();
  		#dev.new(width=3, height=2)
  		#windows(record=TRUE, width=3, height=2)
  		if (input$PlottingVariable == "Ozone") {
  		  #print("trying to plot")
  		  plot(subsettedData$Time, subsettedData$Ozone, type="b",
  		       ylab=outputVar, main=input$PlottingVariable)
  		  #plot_ly(subsettedData, x = ~Time, y = ~Ozone, type="scatter",
  		  #        mode="lines") %>% layout(xaxis=x, yaxis=y)  
  		} else if (input$PlottingVariable == "Temp") {
  		  plot(subsettedData$Time, subsettedData$Temp, type="b",
  		       ylab=outputVar, main=input$PlottingVariable)
  		  #plot_ly(subsettedData, x = ~Time, y = ~Temp, type="scatter",
  		  #        mode="lines") %>% layout(xaxis=x, yaxis=y)  
  		} else if (input$PlottingVariable == "Solar.R") {
  		  plot(subsettedData$Time, subsettedData$Solar.R, type="b",
  		       ylab=outputVar, main=input$PlottingVariable)
  		  #plot_ly(subsettedData, x = ~Time, y = ~Solar.R, type="scatter",
  		  #        mode="lines") %>% layout(xaxis=x, yaxis=y)  
  		} else if (input$PlottingVariable == "Wind") {
  		  plot(subsettedData$Time, subsettedData$Wind, type="b",
  		       ylab=outputVar, main=input$PlottingVariable)
  		  #plot_ly(subsettedData, x = ~Time, y = ~Wind, type="scatter",
  		  #        mode="lines") %>% layout(xaxis=x, yaxis=y)  
  		}
	  }
})


# inputPanel(
#   selectInput("n_breaks", label = "Number of bins:",
#               choices = c(10, 20, 35, 50), selected = 20),
#   
#   sliderInput("bw_adjust", label = "Bandwidth adjustment:",
#               min = 0.2, max = 2, value = 1, step = 0.2)
#   
# )
# 
# renderPlot({
#   hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
#        xlab = "Duration (minutes)", main = "Geyser eruption duration")
#   
#   dens <- density(faithful$eruptions, adjust = input$bw_adjust)
#   lines(dens, col = "blue")
# })
```

## Dataset info
```{r}
colnames(localAQ)
head(localAQ)
```

## To See More...

Go to https://cbrodows.shinyapps.io/shinyApp/ to see the full app in action.

My ui.R and server.R code can be found at:
https://github.com/cbrodows/coursera_ddp_asignment


